\thetitle

### 2022-06-25 thesis/paper.tex
translate paragraph comparing utility model in stable matching vs. my study

The utility model implied by stable assignment differs from that of the present study in two key ways: First, under stable assignment, students' preferences are ordinal rather than cardinal.\footnote{It is possible to estimate cardinal utility values from stable matchings in certain special cases, such as when colleges' preferences are identical and students' preferences are determined by the multinomial logit choice model (Kapur 2021).} Second, stable assignment is deterministic. The student-proposing deferred acceptance algorithm always produces the unique, student-optimal stable assignment. There exist variants of the deferred acceptance algorithm that introduce randomization in order to break ties in schools' preference lists or optimize for distributional goals such as gender parity, but because the randomization occurs after students submit their preferences, it has no effect on the optimal application strategy, which remains to report one's preferences honestly (Ashlagi and Nikzad 2020; Bodoh-Creed 2020). In the admissions process considered in this study, students face a tougher strategic challenge.

>>>>

\ifen 
The utility model implied by stable assignment differs from that of the present study in two key ways: First, under stable assignment, students' preferences are ordinal rather than cardinal.\footnote{It is possible to estimate cardinal utility values from stable matchings in certain special cases, such as when colleges' preferences are identical and students' preferences are determined by the multinomial logit choice model (Kapur 2021).} Second, stable assignment is deterministic: The typical student-proposing deferred acceptance algorithm always produces the unique, student-optimal stable assignment. There exist variants of the deferred acceptance algorithm that introduce randomization in order to break ties in schools' preference lists or optimize for distributional goals such as gender parity, but because the randomization occurs after students submit their preferences, it has no effect on the optimal application strategy, which remains to report one's preferences honestly (Ashlagi and Nikzad 2020; Bodoh-Creed 2020). In the admissions process considered in this study, students face a tougher strategic challenge.
\else
안정 배정 모형에서 말하는 효용의 개념은 본 연구의 효용과 기본적으로 다른 점 2가지 있다. 첫째, 안정 배정에서 학생의 선호 순위는 서수적(ordinal)이며 기수적(cardinal)이 아니다.\footnote{모든 학교의 선호 순위가 동일하고 학생의 선호 순위가 multinomial logit 선택 모형으로 결정되는 경우처럼, 안정 매칭이 주어지면 기수적인 효용 모수를 추정할 수 있는 특수한 경우의 안정 배정이 존재한다 (Kapur 2021).} 둘째, 안정 배정은 결정적인 모형이다: 학생이 학교로 지원하는, 가장 전형적인 DA 알고리즘은 항상 학생에게 최적인 유일한 안정 배정을 출력한다. 확률성을 도입하여 학교 선호 순위의 동점을 처리하거나 성평등 같은 배분적 목적을 최적화하는 DA 알고리즘의 확장이 존재한다. 하지만, 여기서 모든 확률 변수는 학생의 선호 순위를 수집한 다음에 관측되므로 정직한 선호 순위를 신청하는 것이 여전히 학생에게 최적인 지원 전략이다 (Ashlagi와 Nikzad 2020; Bodoh-Creed 2020). 본 논문이 고려하는 입학 과정에서 학생의 지원 전략은 더 어려운 최적화 문제다. 
\fi
